NN_Accel_Heading

### 2024-03-19 Fish Data Analysis/NN_Accel_Heading.qmd
Commit before merge

@@

min_dist <- 0.5 #sd*0.5
max_dist <- 3 #sd*1.5

offset <- 1.5

top_edge <- 3 - offset 
bottom_edge <- 0# + offset
left_edge <- 0 + offset
right_edge <- 7 - offset

#calculate average angle to all other fish in that range
fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
                                                 group_by(Date,Year,Month,Day,Trial,
                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
                                                           #Should be the same number each time
                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T)) %>%
                                                 ungroup()

@@

ggplot(perp_angle_df, aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(0.01, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_classic()+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color))

@@

offset <- 2

top_edge <- 3 - offset 
bottom_edge <- 0# + offset
left_edge <- 0 + offset
right_edge <- 7 - offset

#calculate average angle to all other fish in that range
single_fish_mean_angles <- single_comp_data %>%   #filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light") %>%
                                                filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
                                                #filter(Distance >= min_dist & Distance <= max_dist) %>%
                                                group_by(Date,Year,Month,Day,Trial,
                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
                                                           #Should be the same number each time
                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
                                                           Fish1_X = mean(Fish1_X, rm.na = T),
                                                           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
                                                 ungroup() %>%
                                                 #normalize
                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))

@@

single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df)

@@

effect_size <- mean(single_perp_angle_df$Fish1_Yaw_Heading_PS) / sd(single_perp_angle_df$Fish1_Yaw_Heading_PS)

ggplot(single_perp_angle_df, aes(x = Fish1_Yaw_Heading_PS))+
  geom_histogram(color = "black", fill = "red")+
  theme_classic()

ggplot(single_fish_mean_angles, aes(x = Mean_Angle, y = Fish1_Yaw_Heading_PS))+
  geom_point(color = "red")+
  # geom_smooth(method = "glm", formula = y ~ 1, color = "black")+
  # geom_smooth(method = "glm", formula = y ~ x, color = "green")+
  # geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
  theme_classic()

single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, -0.5),
                                                                      RoundY = round_any(Fish1_Y, -0.5)) %>%
                                                               group_by(RoundX,RoundY) %>%
                                                               summarise(mean_turn = mean(Mean_Angle)) %>%
                                                               ungroup()

@@

>>>>

x_offset <- 1.5
y_offset <- 0.75

max_x <- ceiling(max(fish_comp_data$Fish1_X)) - 1.5
min_x <- floor(min(fish_comp_data$Fish1_X)) - 1.5
max_y <- ceiling(max(fish_comp_data$Fish1_Y)) - 0.75
min_y <- floor(max(fish_comp_data$Fish1_Y)) - 0.75

#Limit away from the edge
fish_comp_data <- fish_comp_data %>% filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
                                     filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge)

@@

min_dist <- 0.5 #sd*0.5
max_dist <- 2 #sd*1.5

#calculate average angle to all other fish in that range
fish_comp_data_ring_angles <- fish_comp_data %>% filter(Distance >= min_dist & Distance <= max_dist) %>%
                                                 #mutate(Mean_Angle = Angle)
                                                 group_by(Date,Year,Month,Day,Trial,
                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                 summarise(Mean_Angle = rad_ang_mean(Angle),
                                                           #Should be the same number each time
                                                           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T)) %>%
                                                 ungroup()

@@

ggplot(perp_angle_df, aes(x = interaction(Ablation, Darkness, sep =", "), y = rad2deg(Fish1_Yaw_Heading_PS),
                          fill = interaction(Ablation, Darkness, sep =", "), color = interaction(Ablation, Darkness, sep =", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = rad2deg(mean_turn)), size = 5, color = "black") +
  geom_errorbar(aes(ymin=rad2deg(mean_turn-sd_turn), ymax=rad2deg(mean_turn+sd_turn)), width=.2, color = "black")+
  theme_classic()+
  ggtitle(paste0("All Neighbors From ",min_dist," to ",max_dist))+
  scale_fill_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_color_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  theme(legend.position = "none")+
  xlab("")+
  ylab("Turning Angle (Degrees / s)")

@@

x_offset <- 1.5
y_offset <- 0.75

top_edge <- 3 - y_offset 
bottom_edge <- 0 + y_offset
left_edge <- 0 + x_offset
right_edge <- 7 - x_offset

#calculate average angle to all other fish in that range
single_fish_mean_angles <- single_comp_data %>%   #filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Light") %>%
                                                filter(Fish1_X >= left_edge & Fish1_X <= right_edge) %>%
                                                filter(Fish1_Y >= bottom_edge & Fish1_Y <= top_edge) %>%
                                                #filter(Distance >= min_dist & Distance <= max_dist) %>%
                                                group_by(Date,Year,Month,Day,Trial,
                                                          Flow,Ablation,Darkness,Type,Flow_Ablation_Darkness,Fish1,Tailbeat_Num) %>%
                                                 # summarise(Mean_Angle = rad_ang_mean(Angle),
                                                 #           #Should be the same number each time
                                                 #           Fish1_Yaw_Heading_PS = mean(Fish1_Yaw_Heading_PS, rm.na = T),
                                                 #           Fish1_X = mean(Fish1_X, rm.na = T),
                                                 #           Fish1_Y = mean(Fish1_Y, rm.na = T)) %>%
                                                 ungroup() %>%
                                                 #normalize
                                                 mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                        Mean_Angle = Angle)

@@

single_perp_angle_df <- rbind(single_perp_angle_df,single_perp_angle_df_neg)

@@

effect_size <- mean(single_perp_angle_df$Fish1_Yaw_Heading_PS) / sd(single_perp_angle_df$Fish1_Yaw_Heading_PS)
effect_size

ggplot(single_perp_angle_df, aes(x = Fish1_Yaw_Heading_PS))+
  geom_histogram(color = "black", fill = "red", binwidth = 1)+
  theme_classic()

ggplot(single_fish_mean_angles, aes(x = Mean_Angle, y = Fish1_Yaw_Heading_PS))+
  geom_point(color = "red")+
  # geom_smooth(method = "glm", formula = y ~ 1, color = "black")+
  # geom_smooth(method = "glm", formula = y ~ x, color = "green")+
  geom_smooth(method = "glm", formula = y ~ sin(x), color = "blue")+
  theme_classic()

single_fish_mean_angles_heatmap <- single_fish_mean_angles %>% mutate(RoundX = round_any(Fish1_X, 0.5),
                                                                      RoundY = round_any(Fish1_Y, 0.5)) %>%
                                                               group_by(RoundX,RoundY) %>%
                                                               summarise(mean_turn = mean(Mean_Angle),
                                                                         n = n()) %>%
                                                               ungroup()

@@

possible_offsets <- expand_grid(x = seq(0,2,0.25), y = seq(0,1.25,0.25))

offset_return <- function(x,y){
  te <- 3 - y 
  be <- 0 + y
  le <- 0 + x
  re <- 7 - x

  tester_data <- single_comp_data %>%  filter(Fish1_X >= le & Fish1_X <= re) %>%
                                        filter(Fish1_Y >= be & Fish1_Y <= te) %>%
                                        mutate(Fish1_Yaw_Heading_PS = Fish1_Yaw_Heading_PS - mean(Fish1_Yaw_Heading_PS, na.rm = T))

  tester_perp_df <- tester_data %>% filter(Angle >= deg2rad(80) & Angle <= deg2rad(100)) %>%
                                                      filter(Flow == "Still Water")

  tester_perp_df_neg <- tester_data %>% filter(Angle >= deg2rad(-100) & Angle <= deg2rad(-80)) %>% 
                                                        filter(Flow == "Still Water") %>% 
                                                        mutate(Fish1_Yaw_Heading_PS = -1*Fish1_Yaw_Heading_PS)

  tester_perp_df <- rbind(tester_perp_df,tester_perp_df_neg)

  t_test_out <- t.test(tester_perp_df$Fish1_Yaw_Heading_PS)

  return(t_test_out$p.val)
}

for(x in seq(0,2,0.25)){
  for (y in seq(0,1.25,0.25)) {
    print(paste(x,y))
    print(offset_return(x,y))
  }
}
